Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-05-23 graviton spectra/content/index.tex
merge

Via this symplectic structure, we can identify the phase space with a twisted cotangent bundle
\[
\cA_M^\bu (\mc V^N) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex]
 \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right) 
\]
For now, the subscript of $\alpha$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.

@@

\[
\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex] 
\ul{-} & \ul{+} \\
\C[w_1,w_2] \{\partial_{w_a}\} \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del^W_\Omega" description] & \C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X}  \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} (\T)\ar[ur, "\del^X_\Omega" description] \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^{0,\bullet}_{X} (\Omega^1) \\ &  \C[w_1,w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{X} 
\end{tikzcd} \right) 
\]

Exactly analogously to the case of $AdS_4\times S^7$, $\Pi$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.

@@

\brian{edit this section to emphasize that we aren't fully characterizing the interacting structure, just free limit.}

@@

Indeed, recall that in equations \eqref{}, \eqref{} we wrote the phase spaces as twisted cotangent bundles, where the nontrivial Poisson tensor was induced by the terms in the differential coming from bracketing with the flux. When we specialize $N=0$, this Poisson tensor vanishes, and there is an additional Lagrangian given by the zero section.

Explicitly these Lagrangians in the phase space are described as follows.
\begin{itemize}
\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $\C$ 
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}

>>>>

Via this symplectic structure, we can identify the phase space with a twisted cotangent bundle
\beqn\label{eqn:cotm2}
\cA_M^\bu (\mc V^N) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex]
 \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right) 
\eeqn
For now, the subscript of $\alpha$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.

@@

\beqn\label{eqn:cotm5}
\Omega^{0,\bullet}_{X} (\mc V_{X}) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex] 
\ul{-} & \ul{+} \\
\C[w_1,w_2] \{\partial_{w_a}\} \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del^W_\Omega" description] & \C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X}  \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} (\T)\ar[ur, "\del^X_\Omega" description] \\
\C[w_1,w_2] \otimes \Omega^{0,\bullet}_{X} \ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^{0,\bullet}_{X} (\Omega^1) \\ &  \C[w_1,w_2] \{\d w_a\} \otimes \Omega^{0,\bullet}_{X} 
\end{tikzcd} \right) 
\eeqn
Analogously to the case of $AdS_4\times S^7$, $\alpha$ here denotes the extra $N$-dependent differential induced by bracketing with the flux, which deforms the cotangent bundle.

@@

@@

Indeed, recall that in equations \eqref{eqn:cotm2}, \eqref{eqn:cotm5} we wrote the phase spaces as twisted cotangent bundles, where the nontrivial Poisson tensor was induced by the terms in the differential coming from bracketing with the flux. When we specialize $N=0$, this Poisson tensor vanishes, and there is an additional Lagrangian given by the zero section.

Explicitly these Lagrangians in the phase space are described as follows.
\begin{itemize}
\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $\C$ 
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
